An Introduction to Data Science in Education in Education Using R

### 2019-09-04 mtsu-workshop-2019.Rmd
update

---
title: "Won’t you be my neighboR?"
subtitle: "An introduction to R for data science in education"
author: "Joshua Rosenberg and Emily Bovee"
date: "2018-05-16"
output:
  xaringan::moon_reader:
    css: [default, metropolis, metropolis-fonts, custom.css]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

@@

# rmarkdown::render("msu-workshop-2019.rmd", output_file = 'index.html')

@@

# #whoami2

.pull-left[
* Dr. Emily Bovee
* Director of Educational Development and Assessment: Marquette University School of Dentistry
* Cat mom
* Primary areas of interest
  * Understanding student motivation in higher education and professional education
  * Data science education 
]

```{r, out.width = "350px", echo = FALSE, fig.align = "center"}
include_graphics("img/ebv.jpg")
```

@@

*The doc is [here](https://github.com/jrosen48/MSU-workshop-2019/blob/master/demo-doc.Rmd) in the repository*

@@

*The doc is [here](https://github.com/jrosen48/MSU-workshop-2019/blob/master/demo-doc.Rmd) in the repository*
---

@@

  - [Doing data science with R](https://r4ds.had.co.nz/) by Wickham and
    Grolemund (2017)
  - [Big magic with R: Creating learning beyond
    fear](https://speakerdeck.com/apreshill/big-magic-with-r-creative-learning-beyond-fear)
    by Hill (2017)
  - [Data science in education](https://github.com/data-edu/data-science-in-education)
  - [R Studio Community](https://community.rstudio.com/)

@@

- [Jesse Mostipak](https://twitter.com/kierisi)
- [Alison Hill](https://twitter.com/apreshill)
- [Hadley Wickham](https://twitter.com/hadleywickham)
- [Daniel Anderson](https://twitter.com/datalorax_)
- [Mara Averick](https://twitter.com/dataandme)
- [Thomas Mock](https://twitter.com/thomas_mock)
- [Angela Li](https://twitter.com/CivicAngela)
- [R4DS community](https://twitter.com/R4DScommunity)
- [#tidytuesday](https://twitter.com/hashtag/TidyTuesday?src=hash)
- [#rstats](https://twitter.com/hashtag/rstats?src=hash)
- [David Robinson](https://twitter.com/drob)
- [Julia Silge](https://twitter.com/juliasilge)
- [Gabriela de Quieroz](https://twitter.com/gdequeiroz)
- [Joshua Rosenberg](https://twitter.com/jrosenberg6432) and [Emily Bovee](https://twitter.com/ebovee09) (of course! :)

@@

The repository for this workshop is [here](https://github.com/jrosen48/MSU-workshop-2019).

@@

# Contact

- [Joshua Rosenberg](mailto:jmrosenberg@utk.edu)
- [Emily Bovee](mailto:emily.a.bovee@gmail.com)

>>>>

---
title: "An Introduction to Data Science in Education in Education Using R"
subtitle: ""
author: "Joshua Rosenberg"
date: "2019-09-05"
output:
  xaringan::moon_reader:
    css: [default, metropolis, metropolis-fonts, custom.css]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

@@

# rmarkdown::render("MTSU-workshop.rmd", output_file = 'index.html')

@@

@@

*The doc is [here](https://github.com/jrosen48/MTSU-workshop/blob/master/demo-doc.Rmd) in the repository*

@@

*The doc is [here](https://github.com/jrosen48/MTSU-workshop/blob/master/demo-doc.Rmd) in the repository*
---

@@

  - [Doing data science with R](https://r4ds.had.co.nz/) by Wickham and
    Grolemund (2017)
  - [Big magic with R: Creating learning beyond
    fear](https://speakerdeck.com/apreshill/big-magic-with-r-creative-learning-beyond-fear)
    by Hill (2017)
  - [Data science in education](https://github.com/data-edu/data-science-in-education)
  - [R Studio Community](https://community.rstudio.com/)
  - [Data Science in Education Using R](https://github.com/data-edu/data-science-in-education)

@@

- [Jesse Mostipak](https://twitter.com/kierisi)
- [Alison Hill](https://twitter.com/apreshill)
- [Hadley Wickham](https://twitter.com/hadleywickham)
- [Daniel Anderson](https://twitter.com/datalorax_)
- [Mara Averick](https://twitter.com/dataandme)
- [Thomas Mock](https://twitter.com/thomas_mock)
- [Angela Li](https://twitter.com/CivicAngela)
- [R4DS community](https://twitter.com/R4DScommunity)
- [#tidytuesday](https://twitter.com/hashtag/TidyTuesday?src=hash)
- [#rstats](https://twitter.com/hashtag/rstats?src=hash)
- [David Robinson](https://twitter.com/drob)
- [Julia Silge](https://twitter.com/juliasilge)
- [Gabriela de Quieroz](https://twitter.com/gdequeiroz)
- [Emily Bovee](https://twitter.com/ebovee09)
- [Joshua Rosenberg](https://twitter.com/jrosenberg6432)

@@

The repository for this workshop is [here](https://github.com/jrosen48/MTSU-workshop).

@@

# Acknowlegment

This presentation is based on one given with Dr. Emily Bovee: https://github.com/jrosen48/MSU-workshop-2019

---
# Contact

- [Joshua Rosenberg](mailto:jmrosenberg@utk.edu)
